Results

### 2025-06-05 index.qmd
docs: update
chore: clean a little

@@

@@

@@

@@

## Comparison of Discontinuity Properties

![](figures/enc2/thickness_current.spi_n_spi.png)

![](figures/enc2/density_distribution.spi_n_spi.png)

![](figures/enc7/properties_distribution.svg)

Thickness and current density relationship
Scale-dependent properties of current sheets in the solar wind

@@

## Alfvénicity

@@

### Estimated Anisotropy

@@

>>>>

@lotekarKineticscaleCurrentSheets2022

@@

> We will also present plasma density estimates delivered by the quasi-thermal noise spectroscopy available at about 7 s cadence (Moncuquet et al. 2020).
> The procedure of CS selection and methodology, briefly described below, is equivalent to those used in the paper

@@

@telloniSpacecraftRadialAlignments2023

@@

# Overview and Example of Current Sheets

> @lotekarKineticscaleCurrentSheets2022 Figure 1 presents an overview of the considered 10 day interval. Over this interval, the spacecraft was at radial distances from 0.17 to 0.24 au, that is, from 35 to 50 solar radii, and remained within the inward magnetic field sector without crossing the heliospheric current sheet (Phan et al. 2020; Szabo et al. 2020). No coronal mass ejections were observed in the considered interval (Phan et al. 2020; Szabo et al. 2020). The spacecraft was approximately corotating with the Sun and connected to the same coronal hole (Bale et al. 2019; Badman et al. 2020). Panels (a)–(d) present 1 minute averages of the magnetic field magnitude, proton flow velocity, densities, and temperatures of protons and electrons as well as plasma density estimates provided by the quasi-thermal noise spectroscopy. The magnetic field magnitude was about 100 nT at the perihelion on November 6, and around 50 nT as the spacecraft moved to a radial distance of 50 solar radii from the Sun on November 1 and 10. The solar wind was typically slow  with a proton flow velocity below 400 km s−1, except for the ≈20 hr period of fast solar wind between November 9 and 10. The three plasma density estimates in panel (c) are consistent with each other within a few tens of percent over the entire interval, except for the fast solar wind interval, where the proton densities were about 4 times smaller than the plasma density estimates provided by the quasi-thermal noise spectroscopy. We will use the electron density estimates, calibrated to best match proton densities and the results of quasi-thermal noise spectroscopy, as plasma density estimates. The proton temperature during the considered interval varied between about 10 and 100 eV, while the electron temperature remained around 30 eV. Panel (e) presents 1 minute averages of proton and electron betas and shows that both quantities varied in the range from 0.1 to 5.
> Figure 2 presents several CSs from our data set.

@@

@@

@@

## Estimated Anisotropy

@@

# Discussion

Thickness and current density relationship, scale-dependent properties of current sheets in the solar wind

### 2025-06-05 notebooks/10_results.qmd
fix: update
chore: clean a little

```{julia}
using Revise
using DrWatson
@quickactivate
include(srcdir("main.jl"))
import Beforerr: easy_save
```

```{julia}
enc = 8 # event id (encounter id)    
easy_save(fname; enc=enc) = Beforerr.easy_save(fname; dir="$fig_dir/enc$enc", formats=[:svg, :pdf])
```

@@

## Discontinuities' properties

@@

```{julia}
begin
    fname = "thickness_current"

    plt = data_layer_a * visual(Scatter)

    fig = Figure(size=(1000, 500))
    axis = log_axis

@@

    grid1 = plt * mapping(l_map, j_map) |> draw!(ga; axis=axis)
    grid2 = plt * mapping(l_norm_map, j_norm_map) |> draw!(gb; axis=axis)

@@

`ggscatterhist` can not handle log scale well

>>>>

```{julia}
using DrWatson
using PSPAnisotropy.Dataset: load_all
using Discontinuity: var_mapping
import Beforerr: easy_save
using GLMakie, AlgebraOfGraphics
m = var_mapping()
```

@@

## Current sheet's properties

@@

### Thickness and current density comparison

```{julia}
begin
    fname = "thickness_current_xy_comp"
    data_layer = data(df)
    plt = data_layer * visual(Scatter)

    fig = Figure(size=(1000, 500))
    axis = (; yscale=log10, xscale=log10)

@@

    spec1 = plt * mapping(m.l, m.j)
    spec2 = plt * mapping(m.l_norm, m.j_norm)

    draw!(ga, spec1; axis)
    draw!(gb, spec2; axis)

@@
